Manuscript

### 2021-08-17 Manuscript/Manuscript_Results.Rmd
update

```{r Setup, include=FALSE}

knitr::opts_knit$set(root.dir = ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd()))

@@

knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	dpi = 400,
	cache = FALSE
)

source(file.path('R', 'Setup.R'))

# The following are already the default, but better be explicit
options(baysren.probs = c(.05, .5, .95))
options(baysren.sessions_folder = 'Sessions')

@@

@@

```{r Results}

@@

```{r Performance, cache = FALSE}

@@

As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a subset of 1200 completely manually labelled records (validation set). The best set of parameters suggested an initial input of 250 labelled records, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval. On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated). A summary of the results of the grid search is reported in Table 3 in Suppl. Mat. S2.

@@

```{r Performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 1. 90% Predictive distribution of the cumulative number of positive matches estimated by the logistic Bayesian models applied to the engine output. The distribution is depicted by the shaded area. The distribution is cut at the level of the observed cumulative distribution of positive matches (red dots), since there cannot be false positive in the dataset and predicted value below this line are not possible."}

>>>>

```{r setup, include=FALSE, message=FALSE, warning=FALSE, error = FALSE}

wd <- ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd())

knitr::opts_knit$set(root.dir = wd)

@@

knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	dpi = 400,
	cache = TRUE,
	cache.rebuild = FALSE
)
# message(wd)
# sys.source(file.path(wd, 'R', 'Setup.R'), envir = knitr::knit_global())

@@

```{r load framework, cache.rebuild=TRUE}
source(file.path('R', 'Setup.R'))

# The following are already the default, but better be explicit
options(baysren.probs = c(.05, .5, .95))
options(baysren.sessions_folder = 'Sessions')
```

@@

```{r results}

@@

```{r performance, cache = FALSE}

@@

As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a subset of 1200 completely manually labelled records (validation set). The best set of parameters suggested an initial input of 250 labelled records with 20x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval. On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated). A summary of the results of the grid search is reported in Table 3 in Suppl. Mat. S2.

@@

```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 1. 90% Predictive distribution of the cumulative number of positive matches estimated by the logistic Bayesian models applied to the engine output. The distribution is depicted by the shaded area. The distribution is cut at the level of the observed cumulative distribution of positive matches (red dots), since there cannot be false positive in the dataset and predicted value below this line are not possible."}
